An open and continuously updated fern tree of life (FTOL)

### 2022-02-04 ms/manuscript.Rmd
Update MS

```{r genbank-make}
fern_tree_sampling <-
	tribble(
		~source, ~year, ~n_species,
		"Hasebe1995", 1995, 107,
		"Schuettpelz2007", 2007, 400,
		"Lehtonen2011", 2011, 2957,
		"Testo2016a", 2016, 3973,
		"this_study", 2021, n_sanger_ferns
	) %>%
	mutate(source = fct_reorder(source, year))

@@

genbank_plot <-
	ggplot(gb_species_by_year, aes(x = year, y = n_species)) +
	geom_line(aes(color = type)) +
	scale_color_manual(values = compartment_cols, guide = "none") +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("nuclear", "mitochondrial")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf)
	) +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("total", "plastid")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf),
		min.segment.length = 0
	) +
	geom_point(
		data = fern_tree_sampling,
		aes(shape = source)
	) +
	labs(shape = "Study", y = "No. species", x = "Year") +
	theme(legend.position = "bottom",
				plot.margin = margin(r = 1, t = 0.5, unit = "in")) +
	coord_cartesian(clip = "off")
```

>>>>

```{r genbank-make}
fern_tree_sampling <-
	tribble(
		~source, ~year, ~n_species, ~label,
		"Hasebe1995", 1995, 107, "Hasebe et al. 1995",
		"Schuettpelz2007", 2007, 400, "Schuettpelz et al. 2007",
		"Lehtonen2011", 2011, 2957, "Lehtonen 2011",
		"Testo2016a", 2016, 3973, "Testo and Sundue 2016",
		"this_study", 2021, n_sanger_ferns, "This study",
	) %>%
	mutate(source = fct_reorder(source, year))

@@

genbank_plot <-
	ggplot(gb_species_by_year, aes(x = year, y = n_species)) +
	geom_line(aes(color = type)) +
	scale_color_manual(values = compartment_cols, guide = "none") +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("nuclear", "mitochondrial")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf)
	) +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("total", "plastid")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf),
		min.segment.length = 0
	) +
	geom_point(
		data = fern_tree_sampling,
		aes(shape = source)
	) +
	scale_shape(
    limits = fern_tree_sampling$source, 
    labels = fern_tree_sampling$label
	) +
	labs(shape = "Study", y = "No. species", x = "Year") +
	theme(legend.position = "bottom",
				plot.margin = margin(r = 1, t = 0.5, l = 0.5, unit = "in")) +
	guides(shape = guide_legend(title.position = "top")) +
	coord_cartesian(clip = "off")
```
